\documentclass[hyp, 12pt]{socreport}
\usepackage{fullpage}

\usepackage{url}
\usepackage{amsmath,amsthm,amsfonts}
\usepackage{algorithm,algorithmic}
\usepackage[dvips]{color}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{CJKutf8}
\usepackage{multicol}
\setlength{\columnseprule}{0.5pt}
\setlength{\columnsep}{20pt}

\usepackage{tikz}
\usetikzlibrary{trees}
\usetikzlibrary[positioning]
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\tikzstyle{level 1}=[level distance=4cm, sibling distance=3.5cm]
\tikzstyle{level 2}=[level distance=4cm, sibling distance=2cm]
\tikzstyle{bag} = [text width=4em, text centered]
\tikzstyle{end} = [circle, minimum width=3pt,fill, inner sep=0pt]
\tikzstyle{fork} = [circle, minimum width=3pt,fill, inner sep=0pt]

\begin{document}
\pagenumbering{roman}
\title{Citation Provenance}
\author{Heng Low Wee \\ (U096901R)}
\projyear{2011/12}
\projnumber{H079820}
\advisor{A/P Min-Yen Kan}
\deliverables{
	\item Report: 1 Volume
	\item Source Code: 1 DVD}
\maketitle
\begin{abstract}
\paragraph{}
We investigate a new task in citation analysis, {\it citation provenance}, to locate the location of the cited information that justifies a citation. We describe the challenges in collecting annotations for our training set, and present a two-tier approach in tackling this problem. We adopted some features used in Citation Classification and Information Retrieval tasks and with them we differentiate citations that referred to the whole paper in general ({\it general}) versus ones the cited specific claims, evidence or parts of the paper ({\it specific}) and then given that a citation is {\it specific}, locate the cited information in the cited paper. The first tier ({\it GvS}) obtained a promising accuracy of $0.786$ in cross-validation evaluation and in terms of $F_1$ score the second tier ({\it LocateProv}), at $0.90$, performed about $25\%$ better than the baseline.

\begin{descriptors}
	\item H. INFORMATION SYSTEMS
\end{descriptors}
\begin{keywords}
	citation analysis, citation provenance, source of citation, citation classification
\end{keywords}
\begin{implement}
\begin{flushleft}
\hspace{5 mm}Software: Python, NLTK\footnote{http://nltk.org/}, scikit-learn\footnote{http://scikit-learn.org/} \nocite{scikit-learn}\\
\hspace{5 mm}Hardware: MacBook Pro, Intel Core 2 Duo 2.4GHz, 4GB Memory.
\end{flushleft}
\end{implement}
\end{abstract}

\begin{acknowledgement}
\paragraph{}
I would like to express my gratitude to all the volunteer participants from the NUS WING group for participating in my pilot annotation tests. I thank them for testing my annotation scheme, and appreciate the feedback that improved my project.

\paragraph{}
Congrats to the \url{CodeForScience} team from WING NUS, consisting of Jin Zhao, Tao Chen, Eric Yulianto Ang and myself for having emerged the winners for the competition with our prototype application CitWeb that integrated our projects -- Citation Classification and Citation Provenance.

\paragraph{}
Million thanks to Jin Zhao, Tao Chen, and especially my supervisor to this project, A/P Min Yen Kan for providing their guidance during the duration of the project.
\end{acknowledgement}

\listoffigures
\listoftables
\tableofcontents

\input{1_introduction}
\input{2_relatedwork}
\input{3_problemanalysis}
\input{4_approach}
\input{5_evaluation}
\input{6_discussion}
\input{7_conclusion} 

\bibliographystyle{socreport}
\bibliography{bibsource}
\appendix
\input{8_appendices}
\end{document}
